251 Rescues

### 2024-02-16 code/process.Rmd
finish first pass analysis

subj |> group_by(replication_score) |> tally()

success <- filter(subj, binary_success==1)

```
* We will report the distribution of subjective replication success in our rescue sample

Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results.

@@

Compute prediction intervals and p_orig, write processed data to file.

```{r}
do_rma <- function(df) {
  if(!any(is.na(df$es))){
  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
  }
  return(tibble(rma_est=NA, rma_se=NA))
}

@@

@@

do_p_orig <- function(es, es_se, rep_es, rep_se){
  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
  }
  return(NA)
}
foo <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
  filter(type!="original") |> 
  group_by(target_lastauthor_year) |> 
  nest() |> 
  mutate(rma_result=map(data, do_rma),
         d_rma_result=map(data, do_d_rma)) |> 
  unnest_wider(rma_result) |> 
  unnest_wider(d_rma_result) |> 
  left_join(orig) |> 
  rowwise() |> 
  mutate(p_orig=do_p_orig(es, es_se, rma_est, rma_se),
         d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))

@@

a) p-original between just the original and rescue,

b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)

c) p-original between the rescue and all other replications.

We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each.

>>>>

tallied <- subj|> group_by(replication_score) |> tally()

tallied 
success <- filter(subj, binary_success==1)

d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")

irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
irr
```
* We will report the distribution of subjective replication success in our rescue sample

Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results (`r pluck(tallied,2,1)` with a score of 0, `r pluck(tallied, 2,2)` with a score of .75, and `r pluck(tallied, 2,3)` with a score of 1). The interrater reliability was `r irr |> round(2)`.

@@

NOTE: can't do p-orig not on SMD scale here b/c tau imputation is in SMD units!!!

## orig v all on p-orig
```{r}
do_rma <- function(df) {
  if(!any(is.na(df$es))){
  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
  }
  return(tibble(rma_est=NA, rma_se=NA))
}

@@

do_p_orig <- function(es, es_se, rep_es, rep_se){
  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
  }
  return(NA)
}

@@

orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
  filter(type!="original") |> 
  group_by(target_lastauthor_year) |> 
  nest() |> 
  mutate(rma_result=map(data, do_rma),
         d_rma_result=map(data, do_d_rma)) |> 
  unnest_wider(rma_result) |> 
  unnest_wider(d_rma_result) |> 
  left_join(orig) |> 
  rowwise() |> 
  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))

orig_v_others |> select(target_lastauthor_year, d_p_orig)

@@

## secondary, original and rescue
a) p-original between just the original and rescue,

```{r}
orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se, res_es=calc_ES, res_es_se=calc_SE) |>

  left_join(orig) |> 
  rowwise() |> 
  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))

orig_v_rescue  |> select(target_lastauthor_year, d_p_orig)

## original v !rescue
b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)

```{r}
orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
  filter(type!="original", type!="rescue") |> 
  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
  group_by(target_lastauthor_year) |> 
  nest() |> 
  mutate(rma_result=map(data, do_rma),
         d_rma_result=map(data, do_d_rma)) |> 
  unnest_wider(rma_result) |> 
  unnest_wider(d_rma_result) |> 
  left_join(orig) |> 
  rowwise() |> 
  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))

orig_v_not_rescue  |> select(target_lastauthor_year, d_p_orig)

## rescue v reps
c) p-original between the rescue and all other replications.

```{r}
rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)

rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
  filter(type!="original", type!="rescue") |> 
  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
  group_by(target_lastauthor_year) |> 
  nest() |> 
  mutate(rma_result=map(data, do_rma),
         d_rma_result=map(data, do_d_rma)) |> 
  unnest_wider(rma_result) |> 
  unnest_wider(d_rma_result) |> 
  left_join(rescue_only) |> 
  rowwise() |> 
  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))

rescue_v_reps |> select(target_lastauthor_year, d_p_orig)

## some predint viz! (this is currently with *no* hetereogeneity, idk what we actually want)
We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each.

```{r}
do_predInt <- function(df){
  if(!is.na(df$es)&!is.na(df$es_se)&!is.na(df$rep_es)&!is.na(df$rep_es_se)){
    a <- Replicate::pred_int(df$es, df$es_se**2,df$rep_es, df$rep_es_se**2)
    return(tibble(low=a$int.lo, high=a$int.hi, inside=a$rep.inside))
  }
  return(tibble(low=NA,high=NA, inside=NA))
}

do_d_predInt <- function(df){
  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
    a <- Replicate::pred_int(df$d, df$d_se**2,df$rep_d, df$rep_d_se**2)
    return(tibble(d_low=a$int.lo, d_high=a$int.hi, d_inside=a$rep.inside))
  }
  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
}

```{r}
orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)

predInts <- parsed_d |> 
  filter(type!="original") |> 
  group_by(target_lastauthor_year) |> 
  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
  left_join(orig) |> 
  group_by(target_lastauthor_year,type) |> 
  nest() |> 
  mutate(pred_int=map(data, do_predInt),
         d_pred_int=map(data,do_d_predInt)) |> 
  unnest_wider(pred_int) |> 
  unnest_wider(d_pred_int) |> 
  unnest_wider(data)

### viz attempts
```{r, fig.height=8, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

orig_scale <- ggplot(predInts |> filter(is.na(d_inside)&!is.na(inside)), aes(x=target_lastauthor_year, y=rep_es, ymin=low, ymax=high, color=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
  geom_point(position=position_dodge(width=.4))+
  geom_point(aes(y=es), color="black", position=position_dodge(width=.4), shape=1)+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="predInts on original scale", x="")

smd_scale <- ggplot(predInts |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
  geom_point(position=position_dodge(width=.4))+
  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="predInts on SMD scale", x="")

```
## predInt with heterogeneity

```{r}
do_d_predInt_het <- function(df){
  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
    yio=df$d
    vio=df$d_se**2
    yir=df$rep_d
    vir=df$rep_d_se**2
    t2=.21**2
    pooled.SE = sqrt(vio + vir + t2)
    PILo.sens = yio - qnorm(0.975) * pooled.SE
    PIHi.sens = yio + qnorm(0.975) * pooled.SE
    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
  }
  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
}

```{r}
orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)

predInts_het <- parsed_d |> 
  filter(type!="original") |> 
  group_by(target_lastauthor_year) |> 
  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
  left_join(orig) |> 
  group_by(target_lastauthor_year,type) |> 
  nest() |> 
  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
  unnest_wider(d_pred_int) |> 
  unnest_wider(data)

### viz attempts
```{r, fig.height=8, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

 ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
  geom_point(position=position_dodge(width=.4))+
  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="predInts on SMD scale", x="")
